---
#title: "<span style='font-size: 20px'>An Animal Crossing Villager Hunt Simulator</style>"
#author: "<span style='font-size: 20px'>Created by @jrosecalabrese</style>"
#date: "Deadline is May 16 2021"
output: 
  html_document:
    theme:       
      version: 4
      bootswatch: minty
editor_options: 
  chunk_output_type: console
runtime: shiny
---
<br>
<div class="card text-white bg-primary mb-3" style="max-width: 90rem;">
  <div class="card-header">An Animal Crossing Villager Hunt Simulator</div>
  <div class="card-body">
Created by `@jrosecalabrese` after playing too much Animal Crossing.
  </div>
</div>

```{r include=FALSE}
# libraries
library(shiny)
library(shinydashboard)
library(shinyWidgets)
library(dplyr)
library(tibble)
library(stringr)
library(ggplot2)
library(shinythemes)
library(rsconnect)
library(knitr)
library(bslib)
library(prettydoc)
library(metathis)
```

```{r setup, include=FALSE}
# Read in data
villagers <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/villagers.csv")
```

```{r include=FALSE}
# do data stuff
villagers$row_n <- NULL
villagers$full_id <- NULL
villagers$url <- NULL

villagers$species_count <- -99 # i know i shouldn't do this 
villagers$species_count <- ifelse(villagers$species == "alligator", 7, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "anteater", 7, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "bear", 15, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "bird", 13, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "bull", 6, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "cat", 23, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "chicken", 9, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "cow", 4, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "cub", 16, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "deer", 10, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "dog", 16, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "duck", 17, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "eagle", 9, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "elephant", 11, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "frog", 18, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "goat", 8, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "gorilla", 9, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "hamster", 8, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "hippo", 7, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "horse", 15, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "kangaroo", 8, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "koala", 9, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "lion", 7, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "monkey", 8, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "mouse", 15, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "octopus", 3, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "ostrich", 10, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "penguin", 13, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "pig", 15, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "rabbit", 20, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "rhino", 6, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "sheep", 13, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "squirrel", 18, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "tiger", 7, villagers$species_count)
villagers$species_count <- ifelse(villagers$species == "wolf", 11, villagers$species_count)
villagers$prob <- (1/35)*(1/villagers$species_count)
villagers$prob <- as.numeric(villagers$prob)
```

```{r echo=FALSE, warning=FALSE, error=FALSE}
# user interface elements and layout
ui <- fluidPage(
  
    meta() %>%
    meta_general(
      application_name = "An Animal Crossing Villager Hunt Simulator"),

    name="An Animal Crossing Villager Hunt Simulator",
    theme = bs_theme(bootswatch = "minty"),
    #titlePanel("How many tickets will it take to find your dreamie?"),
    sidebarLayout(
        sidebarPanel(
            
            # Type in your dreamie
             textInput("name", "Which villager are you looking for?"),
            tags$div(tags$a(href="https://villagerdb.com/villagers?game=nh", 
                            "Find a list of all villagers here!", target="_blank")),
             
            # line break
            br(),
            
            # gives probability for typed villager
            textOutput("greeting", inline=FALSE),    
            
            # line break
            br(),

            # Type in the random seed
             textInput("number", "Type in a random number."),
            #textOutput("random", inline=FALSE),  
            #tags$p("This is the seed that the random number generator will be based on.
                    #Don't put zero or negative numbers."),
            
            # How many tickets do you have?
            #sliderInput(inputId = "n", label = "How many tickets do you have?",
                        #min = 1, max = 10000, value = 10),
                
            # line break
            #br(),
            
            #textInput("n", "How many tickets do you have?"),
              #textOutput("ticket", inline=FALSE),
            
            # How many tickets do you have?
            sliderInput(inputId = "n", label = "How many mystery islands do you plan to visit?",
                        min = 1, max = 10000, value = 10),
              #tags$p("Be warned, you may need a few hundred tickets for this simulator
                     #to give you any results."),
            
            # the source
            #tags$div(tags$a(href=post, 
                            #"I based the simulator on this code from the Heads or Tails blog.", target="_blank")),
            
            # supposed to supress warnings...
            tags$style(type="text/css",
                       ".shiny-output-error { visibility: hidden; }",
                       ".shiny-output-error:before { visibility: hidden; }"),
            
                        tags$div(
                tags$h4(""))),     

        mainPanel(
          plotOutput(outputId = "bars")
                  
    )
))


# server-side computations
server <- function(input, output) 
  {
    # give pure number
    output$greeting <- renderText({
        paste0("For every random island, you have a ", 
               round(villagers$prob[villagers$name == input$name], digits = 4), "% chance of finding ",
               input$name," on that island.") 
        } )
     
    # the bar plot
    output$bars <- renderPlot(
      {
        
        # repeatable pls
        rbinom1 <- repeatable(rbinom, seed = input$number)
        
        
        # most of this is for ggplot2; note the input$x syntax4
        flips <- tibble(flips = rbinom1(n = input$n, 
                                       size = 1, 
                                       prob = 1-villagers$prob[villagers$name==input$name])) %>% 
            mutate(flips = if_else(flips == 1, 
                                   paste0("Islands without ", input$name),
                                   paste0("Islands with ", input$name)))
        
        flips %>% 
            count(flips) %>% 
            ggplot(aes(flips, n, fill = flips)) +
            geom_col() +
            scale_fill_manual(values = c("#78c2ad", "#f3969a")) +
            geom_label(aes(flips, n, label = n), size = 5) +
            theme(legend.position = "none",
                  axis.text = element_text(size = 15)) +
            labs(x = "", y = "") +
            ggtitle(paste0("If you visit ", input$n, " islands and are looking for ", input$name, "...")) +
            theme(plot.title = element_text(hjust = 0.5)) +
            theme(plot.title = element_text(size=22))
      }
    
)
}
# run it all
shinyApp(ui = ui, server = server, options = list(height = 530))
```

<div class="card text-white bg-secondary mb-3" style="max-width: 90rem;">
  <div class="card-header">Good luck!</div>
  <div class="card-body">
Animal Crossing: New Horizons is a game for the Nintendo Switch. In Animal Crossing: New Horizons, you live on and build up a deserted island with a small cast of nonplayable characters ("villagers"). Every once in a while, the player has the opportunity to search for or "hunt" new villagers by going to mystery islands. Players usually go on villager hunts with a very specific villager in mind. Sometimes villager hunts for specific villagers can take a few mystery islands, sometimes thousands. 

This shiny app calculates the odds of finding your favorite villager on any mystery island and simulates how long it will take until you come across your dreamie, based on a random seed of your choosing. This is my first shiny app and was created by following Heads or Tail's shiny tutorial <a href = "https://heads0rtai1s.github.io/2019/12/05/shiny-starter-code/" target="_blank">(link here)</a>.
  </div>
</div>

```{r include=FALSE}
#deployApp(appName="dreamie_sim", account="jrcalabrese")
```